### 2021-03-28 final_report/include/CAMT.tex
no decimals in tables

\begin{itemize}
    \item while GF can parse the SL string in a variety of ways and, as a consequence, return multiple TL linearizations, our program only outputs the first candidate translation, preliminarily discarding trees containing terminal nodes that have no linearization in the TL\footnote{A linearization can be missing, for instance, if a concrete syntax is postprocessed by simply getting rid of an ``illegal'' verb causing compilation problems (cf. Section \ref{grgn})} 
    \item to facilitate the experiments, our standalone has been written so that it can translate several newline-separated sentences at once.
\end{itemize}

@@

To address this problem, the CE module has been modified so that it can try to align individual clauses instead of sentences. 
The idea is to obtain, from each pair of sentence trees to align, a pair of lists of subtrees whose heads are labelled \texttt{root}, \texttt{csubj}, \texttt{ccomp}, \texttt{xcomp}, \texttt{advcl} or  \texttt{acl}\footnote{All these clausal labels are defined in Appendix \ref{a_lab}}.

@@

\begin{table}[h]
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    \textbf{}            & \textbf{DMI (en-it)} & \textbf{CSE (en-sv)} \\ \hline
    \textbf{BLEU-1 to 4} & 55.4          & 61.27         \\ \hline
    \textbf{BLEU-1 to 3} & 62.75         & 67.77         \\ \hline
    \textbf{BLEU-1 to 2} & 70.6          & 74.3          \\ \hline
    \textbf{BLEU-1}      & 79.33         & 80.99         \\ \hline
    \end{tabular}
    \caption[BLEU scores for automatic translations based on the course plans grammars]{BLEU scores obtained by comparing one candidate automatic translation per sentence to a reference translation obtained by making the necessary corrections to the automatically generated ones. Both the initial English sentences and their automatic translations were generated using the two course plans grammars.}
    \label{tbleu}
    \end{table}

>>>>

\begin{itemize}
    \item while GF can parse the SL string in a variety of ways and, as a consequence, return multiple TL linearizations, our program only outputs the first candidate translation, preliminarily discarding trees containing terminal nodes that have no linearization in the TL\footnote{A linearization can be missing, for instance, if a concrete syntax is postprocessed by simply getting rid of an ``illegal'' verb causing compilation problems. In the experiments conducted during this project, this initially happened even with some irregular (but correctly lemmatized!) Italian verbs whose infinitive does not end in ``\textit{-are}'', ``\textit{-ere}'' or ``\textit{-ire}'', such as ``\textit{porre}.'' The Italian morphological dictionary was then modified so to also handle this type of verbs.} 
    \item to facilitate the experiments, our standalone has been written so that it can translate several newline-separated sentences at once.
\end{itemize}

@@

To address this problem, the CE module has been modified so that it can try to align individual clauses instead of sentences. 
The idea is to obtain, from each pair of sentence trees to align, a pair of lists of subtrees whose heads are labelled \texttt{root}, \texttt{csubj}, \texttt{ccomp}, \texttt{xcomp}, \texttt{advcl} or  \texttt{acl}\footnote{All these clausal labels are defined in Appendix \ref{a_lab}.}.

@@

\begin{table}[h]
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    \textbf{}            & \textbf{DMI (en-it)} & \textbf{CSE (en-sv)} \\ \hline
    \textbf{BLEU-1 to 4} & 55         & 61         \\ \hline
    \textbf{BLEU-1 to 3} & 63         & 68         \\ \hline
    \textbf{BLEU-1 to 2} & 70         & 74          \\ \hline
    \textbf{BLEU-1}      & 79         & 81         \\ \hline
    \end{tabular}
    \caption[BLEU scores for automatic translations based on the course plans grammars]{BLEU scores obtained by comparing one candidate automatic translation per sentence to a reference translation obtained by making the necessary corrections to the automatically generated ones. Both the initial English sentences and their automatic translations were generated using the two course plans grammars.}
    \label{tbleu}
    \end{table}
